---
title: "Automatic tools and information for creating and improving R packages"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document relies heavily on two posts:

- [Automatic tools for improving R packages](https://www.r-bloggers.com/automatic-tools-for-improving-r-packages/)
- [How to develop good R packages (for open science)](https://www.r-bloggers.com/how-to-develop-good-r-packages-for-open-science/)


## Creating R package

- [Writing an R package from scratch](https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/)
- [R Package Development Pictorial](http://www.mjdenny.com/R_Package_Pictorial.html)
- [R-packages](http://r-pkgs.had.co.nz/) book by Hadley Wickham 
- [MIT Step by Step Instructions for Creating Your Own R Package](http://web.mit.edu/insong/www/pdf/rpackage_instructions.pdf) by Kim, Martin, McMurry and Halterman
- R package [usethis](https://www.tidyverse.org/articles/2017/11/usethis-1.0.0/) automates several steps described in [R-packages](http://r-pkgs.had.co.nz/)
- [rOpenSci Packaging Guide](https://devguide.ropensci.org/building.html) by rOpenSci community
 
 
## Styling Code
 
- R package [lintr](https://github.com/jimhester/lintr) for static code analysis
- R package [style](https://github.com/r-lib/styler) or the R function `usethis::use_tidy_style()` to prettify code
 
Workflow:
```{r eval=FALSE}
usethis::use_tidy_style()
lintr::lint_package()
```


## Continuous Intergration

- [Travis CI guide](https://docs.travis-ci.com/user/languages/r/#configuration-options) by Travis-CI
- [Advanced guide](https://towardsdatascience.com/travis-ci-for-r-advanced-guide-719cb2d9e0e5) by Sebastian Wolf 

Personal configuration for `.travis.yml` file:
```
language: r
r:
  - oldrel
  - release
  - devel

r_github_packages:
  - jimhester/lintr
  
after_success:
  - R CMD INSTALL $PKG_TARBALL
  - Rscript -e 'covr::codecov()'
  - Rscript -e 'lintr::lint_package()'
```


## Spelling 

- `devtools::spell_check` 
- `spelling::spell_check_package`
 
Workflow:
```{r eval=FALSE}
devtools::spell_check(".")
spelling::spell_check_package(".")
```

## Automatic advice

- R package [`goodpractice`](https://cran.r-project.org/web/packages/goodpractice/index.html)

Workflow:
```{r eval=FALSE}
goodpractice::gp(".")
```


## Static html documentation

- R package [`pkgdown`](https://cran.r-project.org/web/packages/pkgbuild/index.html)
- `pkgdown` [tutorial](https://enpiar.com/2017/11/21/getting-down-with-pkgdown/)

```{r eval=FALSE}
pkgdown::init()
pkgdown::build_site()
```


## GitHub

- [Happy Git and GitHub for the useR](https://happygitwithr.com/)



